\documentclass{article}

\title{Usability Metrics}
\author{Britain Southwick\\Haley Young}
\date{\today}

\begin{document}
\maketitle


\textbf{Conclusion:}\\
\indent Between learnability, efficiency and satisfaction, I would rate satisfaction as the most important usability metric, followed by efficiency and learnability. Because there are similar interfaces for e-commerce (Ebay versus Amazon), the way a customer feels after they use the interface is going to make them come back or leave and find a different interface. \\
\indent From the results, it can easily be seen that the users were overall moderately to highly satisfied with both Amazon and Ebay when it came to creating an account as well as searching for an item \emph{(see Table 3)}. But the big drop in satisfaction was on Ebay when it came to writing a review/leaving feedback. The user usually took at least a minute to find the feedback form and many users chose to give up after about two minutes. Because of this, Ebay got a very bad average score of 1.92 for satisfaction in relation to writing a review/leaving feedback.\\
\indent The second most important usability metric, efficiency, was measured with the timing of each task. When it came to creating an account, Ebay usually had better times only because on Amazon, when a user clicked "start here", they were directed to a general login page and therefore usually missed the fact that they had to move a bubble from "Yes, I have a password" to "No, I am a new customer". Other than this, searching for items was pretty equivalent on both interfaces and the review/feedback issue created a lag in times on Ebay (as discussed above). I would say that since creating an account is a one-time thing, the efficiency of this is not as important as the efficiency of leaving a review/feedback, which could potentially be an issue every time a user buys something.\\
\indent The third usability metric, learnability, was seen with how quickly new users were able to do tasks in relation to proficient users. From the results, it is easy to see that new users' times generally were not much longer than proficient users on all tasks except for creating an account on Amazon. The fact that the page was a general login page created a larger gap in average times between profficient users and new users \emph{(see Table 4 and Table 5)} therefore proving that this task is not as easily learnable as the others. But overall, learnability turns out to be done extremely well on both interfaces.\\
\indent So in conclusion, Amazon performed better on all three of these metrics even though it had one slight problem with creating a new account. Therefore I would have to say that Amazon performed better than Ebay.\\

\newpage

\begin{table}
\centering
\begin{tabular}{|l|l|l|l|l|l|l|l|}
  \hline
  \emph {Name} & \emph{Familiar?} & \emph{Account} & \emph{Score} & \emph{Search} & \emph{Score} & \emph{Review} & \emph{Score}\\
  \hline
  Jonathan & No & 10.2 & 4 & 15.3 & 8 & 70.0(Give Up) & 1\\
  \hline
  Danny & Yes & 6.9 & 6 & 17.7 & 5 & 51.2 & 2\\
  \hline
  Tyler & No & 12.4 & 9 & 13.5 & 7 & 168.0(Give Up) & 1\\
  \hline
  Eric & Yes & 7.7 & 8 & 48.1 & 8 & 176.0(Give Up) & 1\\
  \hline
  Masao & Yes & 12.4 & 8 & 23.1 & 8 & 153.0 & 2\\
  \hline
  Marino & Yes & 23.7 & 8 & 9.1 & 10 & 114.0 & 2\\
  \hline
  Haley & No & 15.2 & 7 & 19.4 & 8 & 66.0 & 4\\
  \hline
  Alec & Yes & 10.2 & 9 & 11.3 & 10 & 110.0(Give Up) & 1\\
  \hline
  Olivia & Yes & 12.8 & 10 & 37.6 & 6 & 168.0(Give Up) & 1\\
  \hline
  Quin & Yes(more) & 7.1 & 7 & 12.4 & 7 & 67.0 & 4\\
  \hline
  Braus & Yes & 8.0 & 5 & 12.5 & 8 & 187.0 & 2\\
  \hline
  Marvin & Yes & 21.7 & 5 & 29.4 & 8 & 52.9 & 3\\
  \hline
  Teresa & Yes & 14.0 & 10 & 26.9 & 7 & 101.0 & 1\\
  \hline
\end{tabular}
\caption{This table shows the times for tasks on Ebay in seconds and the satisfaction score given to each task}
\end{table}


\begin{table}
\centering
\begin{tabular}{|l|l|l|l|l|l|l|l|}
  \hline
  \emph {Name} & \emph{Familiar?} & \emph{Account} & \emph{Score} & \emph{Search} & \emph{Score} & \emph{Review} & \emph{Score}\\
  \hline
  Jonathan & Yes & 24.1 & 8 & 8.3 & 8 & 7.3 & 9\\
  \hline
  Danny & Yes & 19.4 & 5 & 8.7 & 8 & 13.6 & 5\\
  \hline
  Tyler & No & 45.4 & 9 & 11.5 & 9 & 11.2 & 8\\
  \hline
  Eric & Yes(more) & 18.7 & 7 & 4.9 & 8 & 15.8 & 9\\
  \hline
  Masao & Yes(more) & 25.5 & 9 & 12.3 & 9 & 8.1 & 10\\
  \hline
  Marino & Yes(more) & 26.5 & 8 & 9.6 & 10 & 8.7 & 8\\
  \hline
  Haley & No & 62.0 & 5 & 10.0 & 8 & 12.6 & 8\\
  \hline
  Alec & Yes & 18.9 & 8 & 7.7 & 10 & 11.9 & 8\\
  \hline
  Olivia & Yes & 13.6 & 10 & 18.7 & 10 & 19.4 & 10\\
  \hline
  Quin & Yes & 14.7 & 5 & 15.3 & 7 & 21.1 & 8\\
  \hline
  Braus & Yes(more) & 34.1 & 7 & 13.1 & 8 & 70.0 & 7\\
  \hline
  Marvin & Yes & 26.7 & 7 & 20.5 & 8 & 5.8 & 9\\
  \hline
  Teresa & Yes & 25.9 & 9 & 22.6 & 10 & 5.9 & 9\\
  \hline
\end{tabular}
\caption{This table shows the times for tasks on Amazon in seconds and the satisfaction score given to each task}
\end{table}

\begin{table}
\centering
\begin{tabular}{|l||l|l|}
  \hline
  \emph {Measurement} & \emph{Ebay} & \emph{Amazon}\\
  \hline
  Account & 12.48 & 27.35\\
  \hline
  Score & 7.38 & 7.46\\
  \hline
  Search & 21.25 & 12.55\\
  \hline
  Score & 7.69 & 8.69\\
  \hline
  Review & 114.16 & 16.26\\
  \hline
  Score & 1.92 & 8.31\\
  \hline
\end{tabular}
\caption{This table shows the combined averages for the tasks for Ebay and Amazon}
\end{table}

\begin{table}
\centering
\begin{tabular}{|l||l|l|}
  \hline
  \emph {Measurement} & \emph{Ebay} & \emph{Amazon}\\
  \hline
  Account & 12.6 & 53.7\\
  \hline
  Score & 6.67 & 7.0\\
  \hline
  Search & 16.07 & 10.75\\
  \hline
  Score & 7.67 & 8.5\\
  \hline
  Review & 101.33 & 11.9\\
  \hline
  Score & 2.0 & 8.0\\
  \hline
\end{tabular}
\caption{This table shows the Learnability and Satisfaction averages for the tasks for Ebay and Amazon}
\end{table}

\begin{table}[htbp]
\centering
\begin{tabular}{|l||l|l|}
  \hline
  \emph {Measurement} & \emph{Ebay} & \emph{Amazon}\\
  \hline
  Account & 12.45 & 22.55\\
  \hline
  Score & 7.6 & 7.55\\
  \hline
  Search & 22.81 & 12.88\\
  \hline
  Score & 7.7 & 8.73\\
  \hline
  Review & 118.01 & 17.05\\
  \hline
  Score & 1.9 & 8.36\\
  \hline
\end{tabular}
\caption{This table shows the Efficiency and Satisfaction averages for the tasks for Ebay and Amazon}
\end{table}




\end{document}


